Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-03 Paper/ms.tex
orbits
Parameter table

>>>>

\section{Inference}

The unknown parameters are:
\begin{eqnarray}
\left\{N, \boldsymbol{\alpha}, \{\boldsymbol{\phi}\}_{i=1}^N, y_0, s, \nu\right\}
\end{eqnarray}
where $\boldsymbol{\alpha} = \{\mu_T, \sigma_T, \mu_A\}$ are the
hyperparameters, and $\phi_i = \{\}$ are the properties of planet $i$.

In previous studies, the inference was performed by doing separate runs, one
for each possible value of $N$, and calculating the marginal likelihood
$p(\boldsymbol{D} | N)$ as a function of $N$.

\begin{table*}
\begin{tabular}{|c|c|c|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
$N$		& Number of planets	& Discrete Uniform$(0, 10)$\\
\hline
		&	Hyperparameters	&	\\
$\mu_T$		&			&	\\
\end{tabular}
\end{table*}

\section{Orbit Simulations}

The equations of motion were
\begin{eqnarray}
\ddot{x} &=& -\frac{x}{r^3} \\
\ddot{y} &=& -\frac{y}{r^3} \\
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$. The initial conditions
$\{x(0), y(0), \dot{x}(0), \dot{y}(0)\} = \{1, 0, 0, v\}$.
